%==================== ATS FRIENDLY RESUME ====================
% Compile with: pdflatex Akash_Sarwade_Resume.tex

\documentclass[11pt,a4paper]{article}

%-------------------- Packages --------------------
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{lmodern}   % <-- ADD HERE
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage[scaled]{helvet}
\renewcommand{\familydefault}{\sfdefault}

%-------------------- Colors --------------------
\definecolor{darkpurple}{HTML}{4B0082} % Dark Purple (ATS-safe)

%-------------------- Formatting --------------------
\setlength{\parindent}{0pt}
\setlist[itemize]{noitemsep, topsep=2pt}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

%-------------------- Document --------------------
\begin{document}

%-------------------- Header --------------------
\begin{center}
\textbf{\LARGE Akash Sarwade}\\
Software Engineer | Java \& Spring Boot Developer\\
Baner, Pune | +91-9356790044 | 
\href{mailto:akashsarwade18@gmail.com}{akashsarwade18@gmail.com} | 
\href{https://www.linkedin.com/in/akash-sarwade-523b78139/}{LinkedIn}
\end{center}
%-------------------- Summary --------------------
\section*{Professional Summary}
Java Developer with 4+ years of experience in designing, developing, and supporting scalable enterprise applications using Java, Spring Boot, and Microservices. Proven expertise in REST API development, production issue troubleshooting, and end-to-end Root Cause Analysis (RCA). Strong experience in CI/CD automation, AWS cloud services, and monitoring using ELK Stack. Effective collaborator in Agile environments with a strong focus on reliability and performance.

%-------------------- Skills --------------------
\section*{Technical Skills}
\textbf{Languages:} Java \\
\textbf{Frameworks:} Spring Core, Spring MVC, Spring Boot, Hibernate/JPA, Microservices, REST APIs \\
\textbf{Frontend:} JavaScript (Basic), React.js (Basic) \\
\textbf{Databases:} Oracle, MySQL, SQL Server \\
\textbf{Cloud:} AWS (S3, SNS) \\
\textbf{Servers:} Apache Tomcat, JBoss \\
\textbf{DevOps \& Tools:} Git, Maven, Jenkins, Bitbucket, Rancher, Concourse, SonarQube, Postman, Jira, Confluence \\
\textbf{Messaging \& Monitoring:} IBM MQ, MQ Visual Edit, Apache Kafka, ELK Stack, Kibana

%-------------------- Experience --------------------
\section*{Professional Experience}

\textbf{\textcolor{darkpurple}{Accenture Solutions Pvt. Ltd.}} \hfill Pune\\
\textit{Application Development Analyst} \hfill

\textbf{Comcast Corporation} \hfill May 2025 -- Present
\vspace{6pt}
\begin{itemize}
  \item Investigated and resolved production defects in \textbf{WkflBillingOrder} microservice across multiple environments.
  \item Performed detailed RCA by analyzing workflow failures, order fallout data, and domain-level updates.
  \item Implemented permanent code fixes to improve workflow stability and reduce repeat incidents.
  \item Automated build and deployment pipelines using Jenkins CI/CD.
  \item Managed Git branching, pull requests, and release merges.
  \item Collaborated with QA, operations, and architecture teams for fix validation.
  \item Authored RCA and troubleshooting documentation for cross-team knowledge sharing.
\end{itemize}
\vspace{6pt}
\textbf{QRG (Supply Chain Management)} \hfill Jul 2024 -- Apr 2025
\vspace{6pt}
\begin{itemize}
  \item Designed and executed BDD test scenarios using Gherkin for Trailer Management Service.
  \item Optimized CI/CD pipelines (Bitbucket → Jenkins → Rancher).
  \item Implemented monitoring and alerting using Kibana dashboards and Watcher.
  \item Built reusable libraries for dynamic base URL and warehouse configuration management.
  \item Developed utility modules for date/time validation and formatting.
  \item Participated in Agile sprint ceremonies and maintained Confluence documentation.
\end{itemize}


\textbf{\textcolor{darkpurple}{DXC Technology}} \hfill Feb 2022 -- Jun 2024\\
\textit{Software Analyst}

\vspace{6pt}
\textbf{HPE Profile Allocation}

\begin{itemize}
  \item Developed middleware integration between EDIH and Salesforce using Java.
  \item Consumed event notifications via AWS SNS and processed JSON files from AWS S3.
  \item Implemented asynchronous processing and persisted data into SQL Server.
  \item Integrated Java services with Salesforce for downstream business workflows.
\end{itemize}

\vspace{6pt}
\textbf{ Lenovo -- MDM Domain}
\begin{itemize}
  \item Designed and developed REST APIs for business entities such as Account, Contact, and Territory.
  \item Integrated APIs with Apache Kafka for event-driven processing.
  \item Ensured production readiness through testing, deployment, and monitoring.
  \item Implemented CI/CD pipelines for automated build and deployment.
  \item Created detailed RCA and troubleshooting documentation.
\end{itemize}

%-------------------- Certifications --------------------
\section*{Certifications}
\begin{itemize}
  \item AWS Certified Developer – Associate
  \item Oracle Certified Foundations Associate – Java
  \item Profound Training Institute, Pune (4-Month Professional Course)
\end{itemize}

%-------------------- Education --------------------
\section*{Education}
\textbf{Bachelor of Engineering (Computer Engineering)}\\
Savitribai Phule Pune University \hfill 2017 -- 2020\\
\textbf{Diploma in Computer Engineering}

%-------------------- Languages --------------------
\section*{Languages}
English, Hindi, Marathi

\end{document}
